Different rules for binocular combination of luminance flicker in cortical and subcortical pathways

### 2023-06-11 manuscript.Rmd
Downloading all preprocessed files in a zip for speed and avoiding OSF download errors for single files

# check which packages are installed, install the missing ones, and activate
packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','png','tiff','pals','ez','gtools','signal','boot','quickpsy','rstan','coda','parallel','osfr') # list of CRAN packages
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
if (!'FourierStats' %in% installed.packages()[,1]){remotes::install_github("bakerdh/FourierStats")}
packagelist <- c(packagelist,'FourierStats')
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

@@

if (!file.exists(paste0(datadir,'headerfile.csv'))){
# copy from resources folder
file.copy('resources/headerfile.csv',paste0(datadir,'headerfile.csv'))
}

if (!file.exists(paste0(localdir,'StimulusExample.png'))){
# copy from resources folder
file.copy('resources/StimulusExample.png',paste0(localdir,'StimulusExample.png'))
}

>>>>

# check which packages are installed, install the missing ones, and activate
packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','png','tiff','pals','ez','gtools','signal','boot','quickpsy','rstan','coda','parallel','utils','osfr') # list of CRAN packages
missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
if (length(missingpackages)>0){install.packages(missingpackages)}
if (!'FourierStats' %in% installed.packages()[,1]){remotes::install_github("bakerdh/FourierStats")}
packagelist <- c(packagelist,'FourierStats')
toinstall <- packagelist[which(!packagelist %in% (.packages()))]
invisible(lapply(toinstall,library,character.only=TRUE))

@@

if (processdata>0){
if (!file.exists(paste0(datadir,'headerfile.csv'))){
# copy from resources folder
file.copy('resources/headerfile.csv',paste0(datadir,'headerfile.csv'))
}

if (!file.exists(paste0(localdir,'StimulusExample.png'))){
# copy from resources folder
file.copy('resources/StimulusExample.png',paste0(localdir,'StimulusExample.png'))
}
}

if (processdata==2){
# if we're going to need the pre-processed files, download all in a zip file
  if (!file.exists(paste0(datadir,'P101summary.RData'))){
          osfnode <- '2qu6y'
          osfproject <- osf_retrieve_node(osfnode)
          osffiles <- osf_ls_files(osfproject,n_max=300)
          fid <- which(osffiles$name=='allprocessed.zip')
          osf_download(osffiles[fid,],localdir,progress=TRUE)
          unzip(paste0(localdir,'allprocessed.zip'),exdir=localdir)
          d <- dir(paste0(localdir,'allprocessed'),full.names=TRUE)
          file.copy(d,datadir)
  }
}
